Understanding the impacts of video-guided activities on parent-child interaction

### 2020-03-30 paper/manuscript.Rmd
cleaning up and adding appendix

abstract: |
  Early parenting practices play an important role in shaping the future  outcomes of young children [@Hart1995; @Heckman2006]. 
  In particular, high-quality early interactions and language input appear to  facilitate language learning and result in higher levels of school performance. 
  The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations. 
  Of special interest are the parents of very young children, who are often difficult to reach in other ways. Yet little is known about the effects of communicating to parents through app-based interventions. 
  We showed parents a short video depicting an age-appropriate parent-child activity from a commercial parenting app, and found that the quality of parent-child interactions increases in some ways as a result of the intervention. 
  Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
wordcount         : "4629"

@@

```{r load-exp1-lexical-data, include=F}
e1path = "../parenting_obs_e1/"
#load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting

d = read.csv("../exp1_lexical_diversityAdd.csv") # with Conversational_Turns, but only has 53 subjects !!

@@

# convert types and tokens to rate: types/min and tokens/min
e1ld <- e1ld %>% 
  mutate(types = (types / play_duration), 
         tokens = (tokens / play_duration),
         Conversational_Turns = (Conversational_Turns / play_duration))

@@

```{r load-exp2-lexical-data, echo=F}
e2path = "../parenting_obs_e2/"
load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
e2Age <- d %>% mutate(Age = age) %>%
  select(sid, Age)
e2_parent_ed = table(d$parent_ed) # unscaled parent_ed
#d = read.csv("exp2_lexical_diversity_data.csv")
d = read.csv("../exp2_lexical_diversityAdd.csv")
d <- d %>% left_join(e2Age, by="sid")

e2data <- d %>%
  mutate(condition = as.factor(condition), 
         gender = as.factor(gender),
         video = as.factor(video)) %>%
  select(-X.1, -X)

e2data$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Science Video", "Activity Video"))

@@

#e2_dur = read.csv(paste0(e2path,"joint_attention/parenting_obs_play_duration_E2.csv"))
#e2_dur <- e2_dur %>% mutate(vid_dur=video_duration_sec / 60) %>% # sec / min
#  select(sid, vid_dur)
#e2data <- e2data %>% left_join(e2_dur, by="sid")

e2_play_duration <- read.csv(paste0(e2path,"joint_attention/parenting_obs_play_duration_E2.csv"), header=T)
e2_play_duration$start_sec = with(e2_play_duration, ifelse(is.na(verbalcue_start_sec), 
                                                           play_start_sec, verbalcue_start_sec))
e2_play_duration <- e2_play_duration %>% 
  mutate(play_duration = (play_stop_sec - start_sec) / 60) %>% # sec to min
  select(sid, play_duration)
e2data <- e2data %>% left_join(e2_play_duration, by="sid")

# convert types and tokens to rate: types/min and tokens/min
e2data <- e2data %>% 
  mutate(types = (types / play_duration), 
         tokens = (tokens / play_duration),
         Conversational_Turns = (Conversational_Turns / play_duration))
```

@@

The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes [@Hart1995; @Marchman2008; @Cartmill2013; @HirshPasek2015]. Thus, because of the potential for large downstream effects [@Heckman2006], there is tremendous interest in interventions that change children's language environment. 
And because parents define a large portion of that environment, especially before the onset of formal schooling, parent behavior is a critical locus for such interventions. 
Many effective parenting interventions require large resource investments and require many hours of in-person contact [@Jamaica2014; @PerryPreschool2004; @Leung2018], making implementation at scale a daunting proposition. 
For this reason, many researchers targeting early language are interested in delivering parenting interventions remotely -- through texts, apps, and videos delivered on digital devices. 
But what do parents take away from these short messages about what to do with or how to talk with their children?

@@

A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55, 0.91] for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 89% CI = [-0.11, 0.67] for rate of passive JA episodes (per minute); ICC = 0.66 with 89% CI = [0.32, 0.85] for rate of coordinated JA episodes; ICC = 0.33 with 89% CI = [-0.11, 0.67] for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 89% CI = [0.24, 0.82] for rate (seconds per minute) of coordinated JA episodes.

@@

Parents' child-directed speech during the play sessions was transcribed; child utterances were not considered.
Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2[^3], with any deviations or exploratory analyses noted.
Below we first report the lexical diversity results, followed by the joint attention results.

@@

For each transcript of child-directed speech, the words were lemmatized using ``spacy2`` [@spacy2], and the word *types* (unique words) and *tokens* (total words) were then tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity. 
Although we initially preregistered TTR as our measure of lexical diversity (since it is a simple, commonly used measure), it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity [MTLD; @McCarthy2010]. 
Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here we use the value proposed by @McCarthy2010: 0.720).

@@

modTTR <- stan_glmer(TTR ~ condition * age + (1|video), data=e1ld)
summary(modTTR) # n_eff ~2100 (is n_eff / n = Effective Sample Size (ESS)?)

e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.14  !!!
p_direction(modTTR, effects="all") # orchestra 78.7%
#print_CI(e1TTR)

@@

# predict word types
types_mod <- stan_glmer(types ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld)
summary(types_mod) # nothing 
p_direction(types_mod, effects="all") # condition 80%, age 78, cond*age 84%..

@@

# predict word types
types_modE <- stan_glmer(paste("types", e1model_string), data=e1ld) 
summary(types_modE) 
p_direction(types_modE, effects="all") # EL 82.5% AA 87% genderM 93.2%, parent_ed 93.5% cond:AA 94.5%
get_stan_glmer_reporting_values(types_modE, 'parent_ed') 
get_stan_glmer_reporting_values(types_modE, 'conditionexp:AA')

# predict # of conversational turns - COULD REPORT THIS
modCT <- stan_glmer(Conversational_Turns ~ condition * age + (1|video), data=e1ld)
summary(modCT) 
get_stan_glmer_reporting_values(modCT, "conditionexp") # pd = .96 mean=2.52 [-.20,5.28]
p_direction(modCT, effects="all")
# E1 CT: exp early significant (+ effect)
# E2 CT: age nearly significant (+ effect)
```

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm [@rstanarm]. 
For effects that are at least 95% likely to be non-zero according to the posterior distribution (i.e., probability of direction: *pd*; @Makowski2019), we report estimated coefficients ($\beta$) as well as 89% Bayesian credible intervals (89% CI)[^4], demarcating the range within which 89% of the posterior falls, meaning that given the observed data, the effect has 89% probability of falling within this range.
There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, `r print_CI(e1TTR)`). 
<!-- A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, `r print_CI(e1MTLD)`]), with no predicted influence of age. -->
Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

[^4]: 89% CIs are recommended for Bayesian analyses because unless the effective sample size (ESS) is on the order of 10,000, the 95% credible interval is unstable [@Kruschke2014; @McElreath2018]. Our ESS is approximately 2,100, and thus we go with the tighter, more stable interval.

@@

We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, `r print_CI(e1tokens)`), with parents using more tokens in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence interval (conf. int.): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`, `r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, 95% conf. int.: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`, `r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).

```{r e1tab, echo=F, include=F}
e1 <- e1ld %>% group_by(Condition) %>%
  summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
            "Mean MTLD"=mean(MTLD), MTLDsd=sd(MTLD),
            "Mean types"=mean(types), types.sd=sd(types),
            "Mean tokens"= mean(tokens), tokens.sd=sd(tokens))
names(e1) = c("Condition","TTR (M)", "(sd)", "MTLD (M)", "(sd)", "Types (M)", "(sd)", "Tokens (M)", "(sd)")
kable(e1, digits=2, caption="Lexical diversity measures in Experiment 1.")
```

@@

ttr2 <- e2data %>% group_by(Condition) %>%
  tidyboot_mean(TTR)

e2ttr <- ggplot(ttr2, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + # labels=addline_format(c("Science Video", "Activity Video"))
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2data, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle("Experiment 2") + small_text

mtld2 <- e2data %>% group_by(Condition) %>%
  tidyboot_mean(MTLD)

e2mtld <- ggplot(mtld2, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2data, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("MTLD") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ") + small_text

e2tok <- e2data %>% group_by(Condition) %>%
  tidyboot_mean(tokens)

e2tokens <- ggplot(e2tok, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2data, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Mean Word Tokens per Minute") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ") + small_text

@@

We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video. 
Parents' bid rate was greater in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 89% CI=[`r e1bids['89pLB']`, `r e1bids['89pUB']`]). 
Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA (seconds per minute of play).
There were no notable effects on the rate of episodes nor on the time spent in coordinated or passive JA episodes.
Figure \@ref(fig:JA) (top) shows the mean rate of bids and episodes of JA by condition in Experiment 1.

@@

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR. 
These models included random intercepts per video. 
Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes ($\beta=`r e1pjaRR["ConditionActivity Video:RR"]`$, 89% CI=[`r e1pjaRR['89pLB']`, `r e1pjaRR['89pUB']`]).
However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR:  $\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, 89% CI=[`r e1pjaE['89pLB']`, `r e1pjaE['89pUB']`]).

@@

### Participants. 
`r nrow(e2data)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months 
(`r e2_12to18["Activity Video"]` 12-17.9 month-olds in the Activity Video condition; 
`r e2_12to18["Science Video"]` 12-17.9 month-olds in the Science Video condition; 
`r e2_18to24["Activity Video"]` 18-24 month-olds in the Activity Video condition;
`r e2_18to24["Science Video"]` 18-24 month-olds in the Science Video condition) and their parents participated in the same museum as Experiment 1. 
We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home. 
Forty-nine percent of participants (n = 41) had been exposed to two or more languages as indicated by their parent. 
Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8). 
Sixteen parents reported their child was of Hispanic origin. 
Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = `r e2_parent_ed[3]`), four-year college (n = `r e2_parent_ed[4]`), some graduate school (n = `r e2_parent_ed[5]`), to completed graduate school (n = `r e2_parent_ed[6]`) or declined to state (n = 13).

@@

### Procedure. 
The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session. 
Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.
The coding procedure also matched that of Experiment 1. 
To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages. 
The two coders had a reliability of ICC = 0.81 with 95% confidence interval (CI) = [0.62,0.91] for number of parent bids for JA; ICC = 0.74 with 89% CI = [0.48, 0.88] for number of passive JA episodes; ICC = 0.80 with 89% CI = [0.61, 0.91] for number of coordinated JA episodes; ICC = 0.72 with 89% CI = [0.44, 0.86] for total duration of passive JA episodes, and ICC = 0.88 with 89% CI = [0.75, 0.94] for total duration of coordinated JA episodes.

@@

Parents' child-directed speech was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
We first report preregistered regressions[^5] predicting TTR and number of tokens, as well as an exploratory regression predicting MTLD.
We then turn to preregistered regressions of parental bids for joint attention and the total number of JA episodes.

[^5]: Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some of the below regressions led us to switch to Bayesian regression. Using a Bayesian analysis also has the added benefit of not requiring arbitrary decisions about changing alpha levels to attempt to correct for multiple comparisons (Gelman, 2008).

@@

# Notes: 
# - including (1|sid) never works: "Error: number of levels of each grouping factor must be < number of observations", so we back off to (1|video)
# Predicting lexical diversity based on experimental condition. 
e2TTR_m <- stan_lmer(TTR ~ age * condition + (1 | video), data=e2data) 
summary(e2TTR_m) # conditionexp beta=-.1 89% CI=[-.2,0.0]
e2TTR <- get_stan_glmer_reporting_values(e2TTR_m,"conditionexp") # -.09 [-.15,-.04]
p_direction(e2TTR_m, effects="all") # age 85.6% age:cond 78%

>>>>

abstract: |
  Early parenting practices play an important role in shaping the future  outcomes of young children [@Hart1995; @Heckman2006]. 
  In particular, high-quality early interactions and language input appear to  facilitate language learning and result in higher levels of school performance. 
  The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations. 
  Of special interest are the parents of very young children, who are often difficult to reach in other ways. Yet little is known about the effects of communicating to parents through app-based interventions. 
  We showed parents a short video depicting an age-appropriate parent-child activity from a commercial parenting app, and found that the quality of parent-child interactions increases in some ways as a result of the intervention. 
  Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
wordcount         : "4938"

@@

```{r load-exp1-lexical-data, include=F}
e1path = "../parenting_obs_e1/"

d = read.csv("../language_analyses/exp1_lexical_diversity.csv")

@@

# convert types and tokens to rate: types/min and tokens/min
e1ld <- e1ld %>% 
  mutate(types = (types / play_duration), 
         tokens = (tokens / play_duration),
         TTR = (TTR / play_duration),
         MTLD = (MTLD / play_duration))

@@

```{r load-exp2-lexical-data, echo=F}
e2path = "../parenting_obs_e2/"
load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
e2Age <- d %>% mutate(Age = age) %>%
  select(sid, Age)
e2_parent_ed = table(d$parent_ed) # unscaled parent_ed
d = read.csv("../language_analyses/exp2_lexical_diversity.csv")
d <- d %>% left_join(e2Age, by="sid")

e2ld <- d %>%
  mutate(condition = as.factor(condition), 
         gender = as.factor(gender),
         video = as.factor(video)) %>%
  select(-X.1, -X)

e2ld$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Science Video", "Activity Video"))

@@

#e2_dur = read.csv(paste0(e2path,"joint_attention/parenting_obs_play_duration_E2.csv"))
#e2_dur <- e2_dur %>% mutate(vid_dur=video_duration_sec / 60) %>% # sec / min
#  select(sid, vid_dur)
#e2ld <- e2ld %>% left_join(e2_dur, by="sid")

e2_play_duration <- read.csv(paste0(e2path,"joint_attention/parenting_obs_play_duration_E2.csv"), header=T)
e2_play_duration$start_sec = with(e2_play_duration, ifelse(is.na(verbalcue_start_sec), 
                                                           play_start_sec, verbalcue_start_sec))
e2_play_duration <- e2_play_duration %>% 
  mutate(play_duration = (play_stop_sec - start_sec) / 60) %>% # sec to min
  select(sid, play_duration)
e2ld <- e2ld %>% left_join(e2_play_duration, by="sid")

# convert types and tokens to rate: types/min and tokens/min
e2ld <- e2ld %>% 
  mutate(types = (types / play_duration), 
         tokens = (tokens / play_duration),
         TTR = (TTR / play_duration),
         MTLD = (MTLD / play_duration))
```

@@

The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes [@Hart1995; @Marchman2008; @Cartmill2013; @HirshPasek2015; see @Schwab2016 for a review]. Thus, because of the potential for large downstream effects [@Heckman2006], there is tremendous interest in interventions that change children's language environment. 
And because parents define a large portion of that environment, especially before the onset of formal schooling, parent behavior is a critical locus for such interventions. 
Many effective parenting interventions require large resource investments and require many hours of in-person contact [@Jamaica2014; @PerryPreschool2004; @Leung2018], making implementation at scale a daunting proposition. 
For this reason, many researchers targeting early language are interested in delivering parenting interventions remotely -- through texts, apps, and videos delivered on digital devices. 
But what do parents take away from these short messages about what to do with or how to talk with their children?

@@

A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55, 0.91] for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95% CI = [-0.11, 0.67] for rate of passive JA episodes (per minute); ICC = 0.66 with 95% CI = [0.32, 0.85] for rate of coordinated JA episodes; ICC = 0.33 with 95% CI = [-0.11, 0.67] for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 95% CI = [0.24, 0.82] for rate (seconds per minute) of coordinated JA episodes.

@@

Parents' child-directed speech during the play sessions (mean duration: `r round(mean(e1ld$play_duration), 2)` min) was transcribed; child utterances were not considered.
Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2[^3], with any deviations or exploratory analyses noted.
Below we first report the lexical diversity results, followed by the joint attention results.

@@

For each transcript of child-directed speech, the caregivers' unique word *types* and *tokens* (total words) uttered were tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity. 
Although we initially preregistered TTR as our measure of lexical diversity (since it is a simple, commonly used measure), it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity [MTLD; @McCarthy2010]. 
Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here we use the value proposed by @McCarthy2010: 0.720).

@@

modTTR <- stan_glmer(TTR ~ condition * age + (1|video), data=e1ld)
summary(modTTR) # n_eff ~2100 (is n_eff / n = Effective Sample Size (ESS)?)
diagnostic_posterior(modTTR) # 2500-4100
e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.14  !!!
p_direction(modTTR, effects="all") # orchestra 78.7%
#print_CI(e1TTR)

@@

# predict word types
types_mod <- stan_glmer(types ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld,
                        adapt_delta = .97)
summary(types_mod) # nothing 
p_direction(types_mod, effects="all") # condition 80%, age 78, cond*age 84%..

@@

# predict word types
types_modE <- stan_glmer(paste("types", e1model_string), data=e1ld) 
summary(types_modE) 
p_direction(types_modE, effects="all") # cond 82.5% EL 82.5% AA 87% genderM 93.2%, parent_ed 93.5% cond:AA 94.5%
get_stan_glmer_reporting_values(types_modE, 'parent_ed') 
e1types_condAA = get_stan_glmer_reporting_values(types_modE, 'conditionexp:AA') # ADD THIS TO TEXT

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm [@rstanarm]. 
For effects that are at least 95% likely to be non-zero according to the posterior distribution (i.e., probability of direction: *pd*; @Makowski2019), we report estimated coefficients ($\beta$) as well as 89% Bayesian credible intervals (89% CI)[^4], demarcating the range within which 89% of the posterior falls, meaning that given the observed data, the effect has 89% probability of falling within this range.
There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, `r print_CI(e1TTR)`). 
A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, `r print_CI(e1MTLD)`]), with no predicted influence of age.
Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

[^4]: 89% CIs are recommended for Bayesian analyses because unless the effective sample size (ESS) is on the order of 10,000, the 95% credible interval is unstable [@Kruschke2014; @McElreath2018]. Our ESS ranges from 2,000-5,000, and thus we go with the tighter, more stable interval.

@@

We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the rate of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, `r print_CI(e1tokens)`), with parents using tokens at a higher rate in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)` tokens/min, bootstrapped 95% confidence interval (conf. int.): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`, `r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, 95% conf. int.: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`, `r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).

```{r e1tab, echo=F, include=F}
e1 <- e1ld %>% group_by(Condition) %>%
  summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
            "Mean MTLD"=mean(MTLD), MTLDsd=sd(MTLD),
            "Mean types"=mean(types), types.sd=sd(types),
            "Mean tokens"= mean(tokens), tokens.sd=sd(tokens))
names(e1) = c("Condition","TTR/min (M)", "(sd)", "MTLD/min (M)", "(sd)", "Types/min (M)", "(sd)", "Tokens/min (M)", "(sd)")
kable(e1, digits=2, caption="Lexical diversity measures in Experiment 1.")
```

@@

ttr2 <- e2ld %>% group_by(Condition) %>%
  tidyboot_mean(TTR)

e2ttr <- ggplot(ttr2, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + # labels=addline_format(c("Science Video", "Activity Video"))
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2ld, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle("Experiment 2") + small_text

mtld2 <- e2ld %>% group_by(Condition) %>%
  tidyboot_mean(MTLD)

e2mtld <- ggplot(mtld2, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2ld, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("MTLD") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ") + small_text

e2tok <- e2ld %>% group_by(Condition) %>%
  tidyboot_mean(tokens)

e2tokens <- ggplot(e2tok, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2ld, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Mean Word Tokens per Minute") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ") + small_text

@@

We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video. 
Parents' bid rate was greater in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, `r print_CI(e1bids)`). 
Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA (seconds per minute of play).
There were no notable effects on the rate of episodes nor on the time spent in coordinated or passive JA episodes.
Figure \@ref(fig:JA) (top) shows the mean rate of bids and episodes of JA by condition in Experiment 1.

@@

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR. 
These models included random intercepts per video. 
Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes ($\beta=`r e1pjaRR["ConditionActivity Video:RR"]`$, `r print_CI(e1pjaRR)`).
However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR:  $\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, `r print_CI(e1pjaE)`).

@@

### Participants. 
`r nrow(e2ld)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months 
(`r e2_12to18["Activity Video"]` 12-17.9 month-olds in the Activity Video condition; 
`r e2_12to18["Science Video"]` 12-17.9 month-olds in the Science Video condition; 
`r e2_18to24["Activity Video"]` 18-24 month-olds in the Activity Video condition;
`r e2_18to24["Science Video"]` 18-24 month-olds in the Science Video condition) and their parents participated in the same museum as Experiment 1. 
We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home. 
Forty-nine percent of participants (n = 41) had been exposed to two or more languages as indicated by their parent. 
Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8). 
Sixteen parents reported their child was of Hispanic origin. 
Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = `r e2_parent_ed[3]`), four-year college (n = `r e2_parent_ed[4]`), some graduate school (n = `r e2_parent_ed[5]`), to completed graduate school (n = `r e2_parent_ed[6]`) or declined to state (n = 13).

@@

### Procedure. 
The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session. 
Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.
The coding procedure also matched that of Experiment 1. 
To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages. 
The two coders had a reliability of ICC = 0.81 with 95% confidence interval (CI) = [0.62,0.91] for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.48, 0.88] for number of passive JA episodes; ICC = 0.80 with 95% CI = [0.61, 0.91] for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.44, 0.86] for total duration of passive JA episodes, and ICC = 0.88 with 95% CI = [0.75, 0.94] for total duration of coordinated JA episodes.

@@

Parents' child-directed speech during the play sessions (mean duration: `r round(mean(e2ld$play_duration), 2)` min) was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
We first report preregistered regressions[^6] predicting TTR and number of tokens per minute of play, as well as an exploratory regression predicting MTLD per minute.
We then turn to preregistered regressions of parental bids for joint attention and the total number of JA episodes.

[^6]: Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some of the below regressions led us to switch to Bayesian regression. Using a Bayesian analysis also has the added benefit of not requiring arbitrary decisions about changing alpha levels to attempt to correct for multiple comparisons (Gelman, 2008).

@@

# Notes: 
# - including (1|sid) never works: "Error: number of levels of each grouping factor must be < number of observations", so we back off to (1|video)
# Predicting lexical diversity based on experimental condition. 
e2TTR_m <- stan_lmer(TTR ~ age * condition + (1 | video), data=e2ld) 
summary(e2TTR_m) # conditionexp beta=-.1 89% CI=[-.2,0.0]
e2TTR <- get_stan_glmer_reporting_values(e2TTR_m,"conditionexp") # -.09 [-.15,-.04]
p_direction(e2TTR_m, effects="all") # age 85.6% age:cond 78%
